---
title: Meeting minutes from the Biology Postdoc Cohort at Emory 
author: |
 | Matthew Malishev^1^* & Molly Gallagher^1^   
 |  
 | _^1^ Department of Biology, Emory University, 1510 Clifton Road NE, Atlanta, GA, USA, 30322_
#bibliography:/Users/malishev/Documents/Melbourne Uni/Thesis_2016/library.bib
fontsize: 10
geometry: margin=1in
documentclass: article
linkcolor: blue
urlcolor: blue
citecolor: red
output:
  html_document:
    highlight: tango
    code_folding: hide
    toc: yes
    toc_depth: 2
    number_sections: no
    toc_float: yes
  pdf_document:
    includes:
      in_header: # add .tex file with header content
    highlight: tango
    template: null
    toc: yes
    toc_depth: 2
    number_sections: false
    fig_width: 4
    fig_height: 5
    fig_caption: true
    df_print: tibble 
    citation_package: biblatex # natbib
    latex_engine: xelatex #pdflatex # lualatex
    keep_tex: true # keep .tex file in dir 
  word_document:
    highlight: tango
    keep_md: yes
    pandoc_args: --smart
    #reference: mystyles.docx
    toc: yes
inludes:
  before_body: before_body.tex
subtitle: 
tags:
- nothing
- nothingness
params: 
  dir: "/Users/malishev/Documents/Emory/admin/postdocs/postdoc_meetups"
  date: !r Sys.Date()
  session: !r sessionInfo()  
  version: !r getRversion()
  email: "matthew.malishev@emory.edu"
  doi: https://github.com/darwinanddavis/emory_postdocs
classoption: portrait
# ^['https://github.com/darwinanddavis/UsefulCode'] # footnote
vignette: >
  %\VignetteIndexEntry{Useful R code}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

<script type="text/x-mathjax-config">
  MathJax.Hub.Config({ TeX: { equationNumbers: {autoNumber: "all"} } });
</script>

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\newpage   

Date: `r params$date`  
R version: `r params$version`  
*Corresponding author: `r params$email`  
This document can be found at `r params$doi`  

\  

Session info   

```{r echo=F, echo=F}
params$session
```      

\newpage  

## Overview

This document contains the meeting minutes from the Biology Postdoc Cohort at Emory.  

The group hosts regular meetups to learn about what the postdocs in Biology at Emory are doing, harness cool research skills and tools that everyone uses, foster research overlaps, brainstorm and troubleshoot ideas, discuss weird results that nobody knows the answer to, practise upcoming seminars, and simply build a stronger postdoc culture in Biology at Emory.    

Questions and suggestions welcome at `r params$email`.    

\newpage  

## TO DO list  

- Add attending postdocs to OPE Emory list (Beverly)    
* Come up with a cooler name for the group  
* Other things  
* Aim for a collaborative paper   

### _Next meetup:_ January 4, 2018      

\newpage    

## December 14, 2018  

## _Biosketch of postdocs_  

**Matt Malishev**  
Civitello lab  
Bioenergetics and individual-based modelling of host-parasite dynamics of human schistosome populations; spatial simulation modelling; metabolic theory  

**Molly Gallagher**  
Koelle lab  
Disease ecology; differential equation models; current work focuses on modeling defective interfering particles in influenza

**Aileen Berasategui Lopez**  
Gerardo lab  
The genomic and chemical basis of host-fidelity  

**Caitlin Conn**  
Gerardo lab  
Host range and its genetic basis in a mycoparasite  

**Jeremy Harris**  
Koelle lab   
Current IAV modeling: Passage study modeling, estimating bottleneck sizes  

**Mary Bushman**  
Rustom lab  
Linking within- and between-host dynamics of infectious diseases (modeling)  

**David Nicholson**  
Prinz lab  
"Lifelong Learning Machines" -- continual machine learning algorithms  

**Julien Catanese**    
Jaeger lab    


**Derrick Morton**    
Corbett lab    

  
### Workshop ideas  
IMPACT workshop  
- Impact of science + advancement in research    
Contact: Derrick   

\newpage  

## November 30, 2018  

### Outcomes for postdoc group  
Meetings every second and fourth week    

Talk therapy among working class postdocs  

Intro talks from postdocs to group 

* Lightning, 2-min talk for group  

* New postdocs give a brief intro talk for their first meeting     

Postdoc mentorship group for assisting grad students during qualifying exams  

* Online directory of postdocs showcasing background and expertise. Include non-science background stuff, such as applying for international universities.    
The journal peer review system and open access science  

* Using _bioarXiv_ and pre-prints    
* Open access science  
* Writing a paper on the science peer review system from postdoc perspective   

\newpage  

## November 1, 2018  

#### Ideas for things people want

Collaborate on overlapping research  
Brainstorm ideas  
Present new results  
Practise conference talks  
Writing retreats  
Regular coding/math club  

#### Bigger ideas  

Combine other labs/departments    
- other biology floor levels  
- math/env sciences  
  
\newpage  

## Links and ideas   








